\documentclass[pageno]{jpaper}
%\documentclass[sigconf,screen]{acmart}
\usepackage[pdf]{graphviz}
\usepackage{pgf-umlsd}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{amsfonts}
\graphicspath{ {./figs/} }
\usepackage{framed,color,verbatim}
\usepackage{mathtools}
\usepackage{flushend}
\definecolor{shadecolor}{rgb}{.9, .9, .9}
\newtheorem{remark}{Remark}
\newenvironment{code}%
   {\snugshade\verbatim}%
   {\endverbatim\endsnugshade}

%replace XXX with the submission number you are given from the ASPLOS submission site.
\newcommand{\asplossubmissionnumber}{XXX}

\usepackage[normalem]{ulem}

\begin{document}

\title{A ZK-Based Multi-Blockchain Transaction Layer for Minimal Trust Base}
%\author{Sinka Gao, Guoqiang Li, Hongfei Fu , Heng Zhang}
\newcommand{\dprotocol}{ZK Multi-Blockchain Aggregator }
\date{}
\maketitle
\thispagestyle{empty}
\begin{abstract}
%\dprotocol is a universal firmware that synchronizes states between different smart contracts on different blockchains. 
In the realm of blockchains, synchronization challenges are two-folded. First, contracts from different blockchains cannot communicate with each other that makes it hard to establish a trustworthy communication channel to share and maintain a universal state between each other. Second, transactions on different blockchains can hardly be ordered and thus interference is common and we need a novel way to avoid and handle interference. Traditional solutions involving third parties have safety and liveness issues and thus need to compromise between safety, permissionless, and liveness.  \dprotocol is a multi-blockchain execution layer that leverages the power of zero-knowledge proof to minimize the trust base of multi-blockchain communication which does not compromise on safety, liveness, permissionless, and atomicity. In contrast to traditional blockchain bridges which perform transactions on different blockchains separately and uses a relay system to enforce the order of transactions and prevent interference, \dprotocol uses an entirely new approach. For each multi-blockchain transaction, \dprotocol simulates the multi-blockchain transactions in its aggregator chain and uses zero-knowledge proofs of the simulation to convince involved blockchains to update their local state accordingly.  On top of this layer, rich applications over multi-blockchains can run safely and efficiently.
\end{abstract}

\input{zkcross/content/introduction}
\input{zkcross/content/prelimiary}
\input{zkcross/content/casestudy}
\input{zkcross/content/protocol}
\input{zkcross/content/properties}
\input{zkcross/content/bench}
\input{zkcross/content/relatedwork}
\bibliographystyle{plain}
\bibliography{main}


\end{document}

